\section*{Ethics, data, funding, and AI-use disclosure}
\noindent\textbf{Data and ethics.} The planned experiments use publicly available,
de-identified databases distributed for research: PTB-XL \cite{wagner2020ptbxl}, the
Chapman--Shaoxing--Ningbo 12-lead ECG database \cite{zheng2020chapman}, and CPSC~2018
\cite{liu2018cpsc}. No new human-subject data
are collected and no identifiable information is used. This methodological study is not clinical
advice.

\noindent\textbf{Funding and competing interests.} No specific funding is currently recorded for
this work. The author reports no competing financial or non-financial interests; both statements
must be reconfirmed at submission.

\noindent\textbf{Development-time AI-tool provenance.} OpenAI Codex and Anthropic Claude Code
assistants were used during repository analysis, code and manuscript review, experiment-workflow
support, and prose editing. An AutoResearchClaw v0.5.0 control configuration was prepared, but the
AutoResearchClaw pipeline did not produce research or review outputs because its required
\texttt{acpx} session disconnected from its queue owner before the Stage~1 prompt completed; the
failed probe produced zero stage artifacts. It must not be credited as having reviewed the paper
unless later successful co-pilot receipts are preserved and authenticated at Stages 5, 9, 15, and
20.

\begin{center}
\fbox{\parbox{0.92\linewidth}{\textbf{Submission disclosure placeholder---complete before
Stage~20.} Record each tool's provider, product, model/version, access date, affected files or
tasks, prompts or run identifiers where policy requires them, and the human verification performed.
Current status: \textsc{Pending provenance-ledger freeze}.}}
\end{center}

AI systems are not authors. The human author remains responsible for study design, source and
citation verification, code execution, statistical interpretation, every numerical value, and the
submitted text. This disclosure must be reconciled with the destination venue's policy before
submission.
