\documentclass{article}
\usepackage{spconf,amsmath,amssymb,graphicx,booktabs,bm}
\usepackage{multirow}
\usepackage[hidelinks]{hyperref}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}

% ---- result macros (auto-generated from results/*.json; do not hand-edit numbers) ----
% target-specific certificate + calibration + baselines; NO fabrication/hallucination.
\input{auto/fair_baselines_macros}

\title{Target-Specific Recoverability Maps for Reduced-Lead ECG Reconstruction}
% Double-blind toggle: flip to \anontrue for a double-blind conference submission; keep
% \anonfalse for the arXiv preprint / camera-ready. Anonymized run hides author + affiliation.
\newif\ifanon\anonfalse
\ifanon
  \name{}\address{}
\else
  \name{Weiping Yan}\address{University of Minnesota, Twin Cities}
\fi

\begin{document}
\maketitle

\begin{abstract}
Reconstructing missing electrocardiogram (ECG) leads from a reduced set is ill-posed, and
a scalar reconstruction error says nothing about \emph{which} named feature's low-rank
(dipolar) component, on \emph{which} lead, is even recoverable. We give a
\emph{target-specific recoverability map}: for a
waveform segment $s$ (P/QRS/ST/T), an observed lead set $S$, and a target lead $\ell$, two
closed-form numbers derived from one truncated SVD of the segment's empirical rank-3 spatial
(``dipolar'') sub-matrix---an \emph{identifiability} $\eta_{s,\ell}(S)$ (zero iff the
target's low-rank component is recoverable from $S$) and a \emph{conditioning}
$\kappa_{s,\ell}(S)$ (its noise/observed-residual gain). The per-lead criterion is the
classical estimability condition specialized to ECG (exact vs.\ a numerical
$\varrho$-truncation, which we separate). The robust findings: precordial ST is \emph{exactly}
non-identifiable from limb leads (the limb leads span the frontal plane, so $\bm M_{s,S}$ has
exact rank 2), and the graded normalized-identifiability ordering is bootstrap-stable for QRS.
For the low-amplitude ST/T segments the fine ordering is \emph{sensitive to the limb-lead
weighting} (a duplicated-limb sensitivity analysis), so we report it with that caveat rather
than as an exact graded claim. We attach distribution-free calibrated intervals for the empirically
predictable residual (conformalized quantile regression, strict fold discipline, honestly
stated within-group coverage), and observe that the total ST-threshold error rate is
empirically similar across the evaluated reconstructors (not a certified bound) while the
false-positive/false-negative split is a reconstructor choice. The map turns ``trust the
reconstruction'' into a per-feature, per-lead, calibrated statement.
\end{abstract}

\begin{keywords}
electrocardiography, inverse problems, identifiability, conformal prediction,
trustworthy machine learning
\end{keywords}

\section{Introduction}
\label{sec:intro}
Wearable and reduced-lead ECG acquisition makes lead \emph{reconstruction} ubiquitous:
recover the standard 12 leads from one, three, or six observed leads
\cite{gradowski2025reveals,cardoso2024bayesian}. A low aggregate error certifies nothing
about \emph{which} morphological features are trustworthy: a cardiologist reads the P wave,
the QRS complex, the ST segment and the T wave, each on specific leads.

We ask a sharper, reconstructor-independent question: \emph{for a given observed lead set,
which target lead's dipolar morphology is even identifiable, and how well-conditioned is its
recovery?} Each waveform segment's instantaneous potential is approximately low rank across
leads; we estimate a per-segment rank-3 spatial basis $\bm M_s$ (top-3 singular vectors of
the population lead covariance). We stress that $\bm M_s$ is a \emph{population-estimated
(PCA)} object: on real PTB-XL its three principal angles to the classical vectorcardiographic
(inverse-Dower) space are graded---one close ($\PhysMinAngLo$--$\PhysMinAngHi^\circ$), one
moderate ($\PhysMidAngLo$--$\PhysMidAngHi^\circ$), and one substantially different
($\PhysMaxAngLo$--$\PhysMaxAngHi^\circ$)---so we call it an empirical rank-3 subspace rather than
a physical dipole (Sec.~\ref{sec:exp}).

\noindent\textbf{Related work and contributions.} Classical work reconstructs missing leads
(regression / VCG synthesis \cite{edenbrandt1988dower,kors1990vcg,nelwan2004reduced}, deep and
arbitrary-mask waveform-completion models \cite{gradowski2025reveals,cardoso2024bayesian,%
lence2025ecgrecover,fang2026imputeecg}) or \emph{selects} optimal leads
\cite{joshi2009sensor}; whether a given target is even recoverable is the classical
estimability question \cite{scheffe1959anova}. Those systems produce a reconstruction; we
instead certify, before any reconstruction, which target is recoverable and attach a graded,
per-target-lead recoverability measure with calibrated per-record error. Our neural baseline is
a \emph{representative} masked-completion U-Net (same family as
\cite{gradowski2025reveals,lence2025ecgrecover}), not a state-of-the-art claim. We do not
claim the underlying identity as new. Our contributions are: (1) a \emph{graded},
per-target-lead recoverability map---continuous $\eta_{s,\ell}(S)$/$\kappa_{s,\ell}(S)$ from a
single truncated SVD that \emph{rank} target leads (not a binary rank test), over an
\emph{empirically-estimated} $\bm M_s$ that differs $43$--$55^\circ$ from the textbook
inverse-Dower dipole, with a truncation-tolerance sensitivity analysis and record-bootstrap
CIs (Sec.~\ref{sec:cert}); (2) a calibration layer attaching distribution-free intervals
(a sound application of conformalized quantile regression + Mondrian \cite{romano2019cqr}, not
a new method) to the map per feature and lead, with strict fold discipline and honest
within-group (not per-diagnosis) coverage (Sec.~\ref{sec:calib}); (3) a graded ST-safety study
on PTB-XL---continuous full-waveform reconstruction shows anterior precordial ST is far from
recoverable from limb leads, with a total ST-threshold error rate empirically similar across
the evaluated reconstructors (an empirical observation, not a certified bound) and a
false-positive/false-negative split that is a reconstructor choice (Sec.~\ref{sec:exp}).

\section{The Recoverability Certificate}
\label{sec:cert}
\input{theorem_corrected}

\section{Distribution-Free Calibration}
\label{sec:calib}
\input{results_v2_calib}

\section{Experiments}
\label{sec:exp}
\textbf{Data.} PTB-XL \cite{wagner2020ptbxl} (21{,}799 twelve-lead records, 100/500\,Hz,
10-fold split) with P/QRS/ST/T delineation by NeuroKit2 \cite{makowski2021neurokit}.

\textbf{Reproducibility.} Code, fixed and deterministic seeds, a pinned dependency manifest, result
lineage (commit / dataset / split hashes in every JSON), and a one-command pipeline are
released\footnote{Anonymized for review; released on acceptance.}; every number in the tables is
regenerated from result JSON (no hand-typed values). The neural baseline is a 24$\to$12-channel
1-D U-Net (base width 64, residual GroupNorm blocks, 60 epochs, Adam $2{\times}10^{-4}$, MSE on
masked leads under random masks, 3 training seeds); the residual predictor is a gradient-boosted
quantile regressor. The map is a deterministic function of the estimated $\bm\mu_s,\bm M_s$
(record-level bootstrap CIs), not a held-out evaluation.
\input{results_v2_maps}
\input{results_v2_baseline}

\section{Conclusion}
Reduced-lead ECG reconstruction has a \emph{known low-rank structure per segment}. Exploiting
it gives a graded per-target-lead recoverability map---what is identifiable, how
well-conditioned, and (via calibration) what interval the predictable residual admits---before
and independent of any reconstructor. It states which lead configurations support recovery of a
feature's low-rank component, e.g.\ that precordial ST is exactly non-identifiable from limb
leads, and reports the empirically similar total ST-threshold error rate the evaluated
reconstructors incur there (dominated by missed, not fabricated, crossings).

\bibliographystyle{IEEEbib}
\bibliography{refs}
\end{document}
