\subsection{Safety case: precordial ST from limb leads}
The certificate warns \emph{before} reconstruction that limb-6$\to$precordial is
unsafe for an ST decision: $\kappa{=}\kapLimb$, effective rank $2$, and the ST segment
is only $\dipST$ dipolar, so precordial ST is largely Tier~III. The danger is real,
\emph{bidirectional}, and RMSE-invisible: over $799$ fold-10 records
(Table~\ref{tab:stemi}), all methods have $\sim\!0.075$\,mV ST error, yet the
generative reconstructor \emph{fabricates} $\stFab$ phantom STEMIs and the conservative
OLS \emph{masks} $\stMask$. Two honest caveats we report rather than hide: (a) even the
dipolar reconstructor---blessed with $h{\equiv}0$---fabricates $\stDipFab$ STEMIs,
because that error lives \emph{inside} the recoverable subspace (a contaminated dipole
estimate) where $h$ is blind; (b) the null-space flag catches only a minority of
generative fabrications ($18/263$, held-out threshold). The dependable safety signal is therefore the
\emph{configuration-level} certificate: this lead set should not drive a precordial ST
call, and $\kappa$ says so with no reconstruction at all.

\begin{table}[t]
\centering
\caption{Limb-6$\to$precordial STEMI failures (PTB-XL fold 10, $799$ records; ST at
J$+$60\,ms vs.\ PR baseline, $0.1$\,mV threshold). RMSE-invisible, bidirectional, and
only partly flaggable---the reliable signal is the upfront $\kappa$ warning.}
\label{tab:stemi}
\small
\begin{tabular}{lccc}
\toprule
method & fabricated & masked & ST err (mV) \\
\midrule
dipolar ($h{\equiv}0$) & 226 & 165 & 0.074 \\
OLS                    & 6   & 360 & 0.075 \\
generative             & 263 & 134 & 0.080 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Guarantees under device shift}
Calibrating on the Schiller CS device family and testing on the AT family (a genuine
within-PTB-XL device shift), the ST/V4 interval keeps nominal $\covCS$ coverage
in-distribution but drops to $\covATplain$ on the shifted device---Tier~II coverage
\emph{is} shift-sensitive. A small ($300$-record) recalibration on the new device
restores it to $\covATrecal$ at a modest width increase ($0.15\!\to\!0.24$\,mV); naive
likelihood-ratio weighting instead over-widens to trivial ($1.00$) coverage and is not
a repair. Tier~I exactness and the Tier~III flag's soundness are unaffected, as
promised: only the Tier~II \emph{level} is shift-sensitive, and it is measurable and
repairable.

\textbf{Cross-dataset.} On the geographically distinct Chapman--Shaoxing database
\cite{zheng2020chapman} ($\crossN$ Chinese hospital records, identical processing), the
data-estimated dipole basis $\bm M_s$ transfers. Per-segment dipolarity matches PTB-XL
(QRS $\crossDipChap$/$\crossDipPtb$, ST $\crossDipSTchap$/$\crossDipSTptb$, T
$\crossDipTchap$/$\crossDipTptb$); the dominant QRS directions align (principal angles
${\le}\crossQRSang^\circ$); and the \emph{well-conditioned} $\kappa_s(S)$ agrees (spanning
$\{$I,II,V1,V3,V5$\}$: $\crossKapSpanChap$ vs $\crossKapSpanPtb$). The lead-mixing operator
$\bm T$ (Einthoven/Goldberger) is dataset-independent by definition; the fit confirms the
estimated $\bm M_s$ is too --- save the lowest-variance dipole direction of the
\emph{less-dipolar} ST/T segments, and the limb-6 configuration, which is effectively
rank-deficient in both cohorts ($\kappa_s{\gtrsim}10^{4}$, its transverse dipole
unobserved and its magnitude numerically unstable).
