\subsection{Baselines and what the map predicts}
Table~\ref{tab:base} reports reconstruction RMSE (mV) of the unobserved target leads under a
\emph{single, identical protocol} for all methods: the same shared split (train folds 1--7,
ridge $\lambda$ selected on fold 8, test on NORM fold-10), the same $\NTestFair$ test records,
per-timepoint waveform RMSE on the same segment indices, and \emph{paired} record-bootstrap
CIs on the step-to-step differences. We include a \emph{representative} masked-completion
baseline---an arbitrary-mask conditional 1-D U-Net trained with random lead masks (one model
serves any configuration, no target-lead leakage), the same family as
\cite{gradowski2025reveals,lence2025ecgrecover,fang2026imputeecg}, run over three seeds
(mean reported)---not a state-of-the-art claim.

On a dipole-spanning set the methods form \LadderQual{}---prior-mean $\to$ dipolar (Tier~I)
$\to$ per-segment ridge (Tier~I+II) $\to$ U-Net---evidence of recoverable non-dipolar content
(the calibrated Tier~II layer), though the neural model's margin over a simple ridge is small
(QRS $\FairSpanUnetQRS$ vs.\ $\FairSpanRidgeQRS$\,mV on $\{$I,II,V1,V3,V5$\}$; paired
$\Delta$ CI \RidgeUnetSpanCI). On \textbf{limb-6} the U-Net still \emph{lowers} error over the
prior mean (QRS $\FairLimbPriorQRS\!\to\!\FairLimbUnetQRS$)---it recovers the predictable,
largely population-correlated structure---but plateaus at $\FairUnetLimbSpanRatio\times$ its
spanning-set error (paired spanning$\to$limb-6 $\Delta$ CI \SpanLimbUnetCI) and no reconstructor
closes that gap. This residual gap is \emph{consistent with} the unobserved dipolar coordinate
the map's $\eta{>}0$ marks as unidentifiable (we do not decompose the error into projected
components, so we claim consistency, not equality): capacity recovers the predictable part but
not the missing coordinate, so a reconstruction that looked confident about anterior precordial
morphology here would be inventing it. We therefore scope the identifiability claim to the
dipolar component, not to a blanket ``not recoverable.''

\begin{table}[t]
\centering\small
\caption{Reconstruction RMSE (mV) of target leads, QRS segment, under one identical
per-timepoint protocol on NORM fold-10 ($\NTestFair$ test records, shared split). ``dipolar''
= Tier~I; ``ridge'' = per-segment ridge (Tier~I+II); ``U-Net'' = representative masked-completion
baseline (3-seed mean). Best in bold. On limb-6 even the neural baseline plateaus far above its
identifiable-set error. Numbers auto-generated from \texttt{results/fair\_baselines.json}.}
\label{tab:base}
\input{auto/fair_baselines_table}
\end{table}

\textbf{Empirical, not physical, subspace.} On real PTB-XL the estimated $\bm M_s$ shares two
directions with the classical inverse-Dower vectorcardiographic space
\cite{edenbrandt1988dower,kors1990vcg} (principal angles $2$--$6^\circ$) but its third
direction differs materially (max angle $43$--$55^\circ$, bootstrap CIs excluding small
angles). We therefore treat $\bm M_s$ as an \emph{empirical rank-3 spatial subspace}
estimated from the data, not a physical cardiac dipole; all recoverability quantities are stated
with respect to this estimated subspace. This empirical, data-driven subspace---rather than a
fixed physiological transform---is what makes the map dataset-specific and, we verify, stable
across PTB-XL and Chapman for the QRS segment (and robust to the duplicated-limb weighting).